Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-02-27 docs/thesis/chap-cern_math_explorer.tex
Added more characters/categories. Work on document: some drawings, graphics, and added comparison on simplification methods.

@@

\subsection{Development with Lucene/Solr}
This section explains how the described components were implemented in the {\codefont Apache Solr/Lucene} framework.
One focus of our work was to develop a modular system that allowed easily to deploy new heuristics as they were identified.

@@

{\codefont SolrStructuralAnalyzer } is simpler in its workflow: It consits of a {\codefont StructuralPatternsTokenizer} that tries to find occurrences of the predefined patterns in the expression. For each match, it emits a token with the pattern that was found. 
\subsection{Integration with Mathematica}
This section describes some aspects that had to be considered while implementing the integration with Mathematica. Our system uses the {\codefont JLink} library to create a connection with the underlying process {\codefont MathKernel}. The main class for communicating java code and {\codefont Mathematica} is {\codefont KernelLink} and the main used method was {\codefont evaluateToOutputForm(String expr, int pageWidth)} where {\codefont expr} is the expression to be evaluated and {\codefont pageWidth} affects the formatting of the result.

@@

@@

\subsection{Integration with CDS}
Currently the Invenio code-base is being under a deep refactoring and rewriting. CDS currently runs in the stable branch {\codefont master} while the new developments are preferred to be implemented in the new branch {\codefont pu}. 
Our system is deployed as a standalone jar which should be incorporated into a Solr instance. Also, some extra configurations should be added. Details on this can be found in appendix \ref{appendix-conf_files}
The communication between Solr and Invenio was through the library {\codefont solrpy}. 
A demo interface over the new branch was developed to showcase the system, however to have a complete integration with CDS, a more deep work is required.

>>>>

Figures \ref{integrals} and \ref{less_greater} present lists related of characters for two different categories.

\begin{figure}[h!]
	\centering
	\includegraphics[height=2 cm]{figures/integrals.png}
	\caption{List of different types of integral related characters in Unicode}
	\label{integrals}
\end{figure}

\begin{figure}[h!]
	\centering
	\includegraphics[height=2 cm]{figures/greater_less.png}
	\caption{List of different types of grater/less than related characters in Unicode}
	\label{less_greater}
\end{figure}

@@

\section{Development with Lucene/Solr}
This section explains how the described components were implemented in the {\codefont Apache Solr/Lucene} framework.
One focus of our work was to develop a modular system that allowed easily to deploy new heuristics as they were identified.

@@

{\codefont SolrStructuralAnalyzer } is simpler in its workflow: It consits of a {\codefont StructuralPatternsTokenizer} that tries to find occurrences of the predefined patterns in the expression. For each match, it emits a token with the pattern that was found.

\section{Integration with Mathematica}
This section describes some aspects that had to be considered while implementing the integration with Mathematica. Our system uses the {\codefont JLink} library to create a connection with the underlying process {\codefont MathKernel}. The main class for communicating java code and {\codefont Mathematica} is {\codefont KernelLink} and the main used method was {\codefont evaluateToOutputForm(String expr, int pageWidth)} where {\codefont expr} is the expression to be evaluated and {\codefont pageWidth} affects the formatting of the result.

@@

\subsubsection{Expression simplification}
The second feature that we are interested in is automatic expression simplification.
Mathematica includes different transformations of expressions. These include: {\codefont Simplify} which tries to transform a given equation in an equivalent one but in a reduced form, {\codefont FullSimplify} which is similar to the previous one but tries a higher number of heuristics to apply that can simplify expressions further at the expense of more processing time, {\codefont Factor} to factorize polynomials, {\codefont Refine} which simplifies expressions given certain assumptions about the variables, {\codefont TrigReduce} that tries to apply trigonometric identities to simplify the expression, {\codefont FunctionExpand} that tries to expand special functions in terms of sums and products of other elementary functions.

The two functions that are more relevant for our work are {\codefont Simplify} and {\codefont FullySimplify} since they apply most of the other combined methods and do not require additional information.

Table \ref{table_simplifications} presents some sample equations found in some the documents in CDS and the different forms of simplification.

\begin{tabular}{|>{\centering\arraybackslash}m{4cm}|>
{\centering\arraybackslash}m{4cm}|>
{\centering\arraybackslash}m{4cm}|}
\hline
Original Form & {\codefont Simplify} & {\codefont FullSimplify} \\
\hline
\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mn>2</mn> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>+</mo> <mi>Φ</mi> </mrow> <mo>)</mo> </mrow> </mrow> </mfrac> <mo>+</mo> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> </mrow> <mo>=</mo> <mn>0</mn> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>Φ</mi> </mrow> <mo>+</mo> <mn>2</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>2</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mi>Φ</mi> <mo>+</mo> <mn>1</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}     \\
$\frac{\Phi '}{2 (1+\Phi )}+\frac{1}{r}=0$          & $\frac{1}{r}+\frac{\Phi '}{2 \Phi +2}=0$ & $\frac{2}{r}+\frac{\Phi '}{\Phi +1}=0$       \\

\hline
\end{tabular}

@@

\section{Integration with CDS}
Currently the Invenio code-base is being under a deep refactoring and rewriting. CDS currently runs in the stable branch {\codefont master} while the new developments are preferred to be implemented in the new branch {\codefont pu}. 
Our system is deployed as a standalone {\codefont jar} which is added to a Solr instance. Also, some extra configurations should be added. Details on this can be found in appendix \ref{appendix-conf_files}
The communication between Solr and Invenio was through the library {\codefont solrpy}. 
Figure \ref{system_arch} presents the main components of our deployment.

\begin{figure}
\includegraphics[height=4.2 cm]{visio_drawings/architecture.png}
\label{comparison_sw_table}
\caption{High level deployment architecture}
\end{figure}

A demo interface over the {\codefont pu} branch was developed to showcase the system, however to have a complete integration with CDS, a more deep work is required. The demo setup employs the same dataset as used for experimentation.
